Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-08-06 manuscript_res.tex
most recent plotting updates

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=.57]{Images/wis_by_week_horizon.png}
    \caption{Boxplots of weighted interval score (WIS) for the 
    four Bayesian nonlinear ILI models, a baseline model (BASE) and
    an autoregressive integrated moving average model (ARIMA) 
    over all seasons in the simulation study faceted by horizon 
    (x-axis) and season week (y-axis). Horizons include 1-4 week ahead forecasts 
    and weeks include weeks 14, 20, 26, 32, and 38 of the flu season}
    \label{fig:wis_by_week_horizon}
\end{figure}

\begin{table}[hbt!]
\centering
\begin{tabular}{lrrrr}
Model & WIS & MAE & 50\%Coverage  & 95\% Coverage \\ 
  \hline
ASGD & 0.09 & 0.15 & 42 & 91 \\ 
  ASG & 0.13 & 0.18 & 33 & 71 \\ 
  ARIMA & 0.13 & 0.18 & 35 & 68 \\ 
  BASE & 0.15 & 0.20 & 33 & 65 \\ 
  SIRD & 0.15 & 0.23 & 33 & 78 \\ 
  SIR & 0.21 & 0.29 & 20 & 51 \\ 
\end{tabular}
\end{table}

@@

@@

\begin{figure}[hbt!]
\begin{adjustwidth}{-3cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    % \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .45]{Images/state_and_date_lwis.png}
    }
    \end{adjustwidth}
    \caption{}
    \label{fig:state_and_date_lwis}
    % \end{minipage}

>>>>

\begin{figure}[hbt!]
    % \centering
    \includegraphics[scale=.5]{Images/all_sim_res.png}
    \caption{Boxplots of weighted interval score (WIS) for the 
    four Bayesian nonlinear ILI models, a baseline model (BASE) and
    an autoregressive integrated moving average model (ARIMA) 
    over all seasons in the simulation study faceted by horizon 
    (x-axis) and season week (y-axis). Horizons include 1-4 week ahead forecasts 
    and weeks include weeks 14, 20, 26, 32, and 38 of the flu season}
    \label{fig:wis_by_week_horizon}
\end{figure}

% \begin{table}[hbt!]
% \centering
% \begin{tabular}{lrrrr}
% Model & WIS & MAE & 50\%Coverage  & 95\% Coverage \\ 
%   \hline
% ASGD & 0.09 & 0.15 & 42 & 91 \\ 
%   ASG & 0.13 & 0.18 & 33 & 71 \\ 
%   ARIMA & 0.13 & 0.18 & 35 & 68 \\ 
%   BASE & 0.15 & 0.20 & 33 & 65 \\ 
%   SIRD & 0.15 & 0.23 & 33 & 78 \\ 
%   SIR & 0.21 & 0.29 & 20 & 51 \\ 
% \end{tabular}
% \end{table}

\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
Model & WIS & 50\%Coverage  & 95\% Coverage \\ 
  \hline
ASGD & 0.02 & 0.42 & 0.91 \\ 
  ASG & 0.03 & 0.33 & 0.71 \\ 
  ARIMA & 0.03 & 0.35 & 0.68 \\ 
  BASE & 0.03 & 0.33 & 0.65 \\ 
  SIRD & 0.03 & 0.33 & 0.78 \\ 
  SIR & 0.05 & 0.20 & 0.51 \\
\end{tabular}
\end{table}

@@

  \centering
  \includegraphics[width=.49\linewidth, height=6cm]{Images/normal_sq_forecasts_us.png}
\caption{Forecasts 1-4 weeks ahead for US hospitalizations during the 2023 
season for weeks 14, 20, 26, and 32. Forecasts are separated by ILI model, 
and the hospitalization models are all normally distribution. The figure 
includes hospitalization forecasts where ILI is a linear predictor (left) 
and where ILI is a quadratic predictor (right). 50\% predictive intervals 
are pink and 95\% predictive intervals are red.}
\label{fig:normal_flu_forecasts}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{adjustwidth}{-3cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .45]{Images/state_and_date_lwis.png}
    }
    \end{adjustwidth}
    \caption{}
    \label{fig:state_and_date_lwis}
    % \end{minipage}

### 2025-08-06 supplemental_res.tex
most recent plotting updates

\newpage
\section{FluSight forecast competition scoring results} \label{app:A_rwis}

>>>>

\newpage
\section{Model forecast comparison}

\begin{figure}[hbt!]
\centering
\begin{subfigure}
  \centering
  \includegraphics[width=.49\linewidth,height=6cm]{Images/normal_forecasts_us.png}
  % \caption{A subfigure}
  % \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}
  \centering
  \includegraphics[width=.49\linewidth, height=6cm]{Images/normal_sq_forecasts_us.png}
  % \caption{A subfigure}
  % \label{fig:sub2}
\end{subfigure}
\caption{Forecasts 1-4 weeks ahead for US hospitalizations during the 2023 
season for weeks 14, 20, 26, and 32. Forecasts are separated by ILI model, 
and the hospitalization models are all normally distribution. The figure 
includes hospitalization forecasts where ILI is a linear predictor (left) 
and where ILI is a quadratic predictor (right). 50\% predictive intervals 
are pink and 95\% predictive intervals are red.}
\label{fig:normal_flu_forecasts}
\end{figure}

    % \centering
    \includegraphics[scale = .6]{Images/lwis_ln_us_full_season.png}
    \caption{Each plot shows the log weighted interval score (LWIS) for every 
    week of the 2023 flu season with scores for models including and exluding 
    discrepancy in the ILI model. Scores are separated by hospitalization 
    distribution family and by ILI as a linear or quadratic predictor. Scores 
    for models with an ASG ILI model are above while those with an SIR model 
    are below. The lower the LWIS the better the forecast.}
    \label{fig:us_lwis}
\end{figure}

% \begin{figure}
%     
%     % \centering
%     \includegraphics[scale = .5]{Images/lwis_us_full_season.png}
%     \caption{Each plot shows the log weighted interval score (LWIS) for every week of the 2023 flu season with scores for models including discrepancy in the ILI model (top) and excluding discrepancy (bottom). Scores are separated by hospitalization distribution family and by ILI as a linear or quadratic predictor. Scores for models with an ASG ILI model are above while those with an SIR model are below. The lighter the shade, the lower the LWIS with low LWIS being better.}
%     \label{fig:us_lwis}
% \end{figure}

    \centering
    \includegraphics[scale = .7]{Images/lwis_by_dist_loc.png}
    \caption{Each plot shows the log weighted interval scores (LWIS) for all 50 
    US states, PR, DC, and national level forecasts at each week during the 
    2023 flu season. Scores are averaged over all horizons 1-4 weeks ahead. 
    Scores are faceted by hospitalization model distribution. The lighter the 
    shade, the lower the LWIS with low LWIS being better.}
    \label{fig:lwis_by_dist_loc}
\end{figure}

Figure \ref{fig:lwis_by_dist_loc} also shows weekly forecast performance by 
LWIS, but all 53 locations are included. The LWIS is shown across the whole 
season faceted by hospitalization model distribution. Overall, the weeks 
leading up to week 22 are the most difficult to forecast, but the LNORM model 
appears to perform the better than the other models during the weeks around 
the holiday week 22. 
The overall, calculated as the mean LWIS over all locations and weeks, for all 
24 models is shown in table \ref{tab:forecast_scores}. The first main takeaway 
is that the top four performing models are SIR ILI models with the LNORM 
hospitalization models. The next main takeaway is that overall the models 
which include discrepancy outperformed the models without discrepancy.

\begin{table}
\caption{Overall scores for each of the 24 forecast models. The overall score 
is the log weighted interval score (LWIS) averaged over all locations, weeks, 
and horizons. The scores in the first two rows are for linear models, and the 
scores in the third and fourth rows are for quadratic models. The lowest WISs 
are bolded.}
\begin{tabular*}{\textwidth}
{@{\extracolsep{\fill}} 
    l*{9}{c}}
  & & \multicolumn{3}{c}{ASG} 
  & \multicolumn{3}{c}{SIR} \\ 
  \cmidrule{3-5} \cmidrule{6-8}
  & & LNORM & LST & NORM & LNORM & LST & NORM\\
  \midrule
  Linear & No Disc & 0.366 & 0.392 & 0.365 & \textbf{0.355} & 0.416 & 0.394 &\\ 
   & Disc & 0.358 & 0.391 & 0.365 & \textbf{0.343} & 0.382 & 0.354 &\\
  \midrule
  Quadratic & No Disc & 0.366 & 0.398 & 0.377 & \textbf{0.355} & 0.401 & 0.377 &\\ 
   & Disc & 0.358 & 0.390 & 0.369 & \textbf{0.343} & 0.378 & 0.356 &\\     
  \bottomrule
\end{tabular*}
\label{tab:forecast_scores}
\end{table}

\section{FluSight forecast competition scoring results} \label{app:A_rwis}
